---
title: "Google Summer of Code 2021"
author: "Mayur Shende"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Organisation: The R Project for Statistical Computing

### Project: Automated (AutoML) tool to clean univariate time series at microscales

#### Tests

-   Easy: Download the `imputeTestbench` package and demonstrate it with a naturally occurring time series. Document it with RMarkdown.

-   Medium: Suggest possible updates or a new feature you would like to include in the next version of the `imputeTestench` package.

-   Hard: Develop a dummy code of 5 functions and a vignette and pass it with no Error/Warning/Note through <https://win-builder.r-project.org/>

#### Easy Test

Install the `imputeTestbench` package using `install.packages("imputeTestbench")` and load it.

```{r echo=TRUE}
library(imputeTestbench)
library(imputeTS)
```

Load temperature dataset. The dataset contains \~5 years of **high temporal resolution** (hourly measurements) temperature data from Vancouver, Canada. (<https://www.kaggle.com/selfishgene/historical-hourly-weather-data?select=wind_speed.csv>)

```{r echo=TRUE}
library(readr)
temperature <- read_csv("temperature.csv")
summary(temperature)
```

Use `imputeTestbench` to compare various imputation methods

```{r echo=TRUE, cache=TRUE}
errs <- impute_errors(temperature$Vancouver, methods = c("na_interpolation", "na_locf", "na_ma", "na_kalman"), missPercentFrom = 10, missPercentTo = 50)
data.frame(errs)
plot_errors(errs, plotType = "line")
```

#### Medium Test

`imputeTestbench` is a great package for comparing various methods of imputation. Few updates that I would suggest are:

-   Introducing new sampling methods such as monte carlo.

-   Making the package interactive.

-   Developing a ShinyApp for the package.

#### Hard Test

For the final test, I created a R package called `Calculator`. It contains five functions, `add()`, `substract()`, `multiply()`, `divide()` and `modulo()` , with documentation and tests. Then, using `devtools::check()`, I checked for any errors or warning, and uploaded the source file to <https://win-builder.r-project.org/>. It passed without errors/warnings/note.

The result of [<https://win-builder.r-project.org/>](https://win-builder.r-project.org/){.uri} is included in the github repository(`00check.log`).
